Inference for Trans-dimensional Bayesian Models with Diffusive Nested Sampling

### 2015-10-28 Documents/Paper/ms.tex
Updated numbers

The marginal likelihood estimate returned by DNS for this data was
$\log(\mathcal{Z}) = -319707.6$, and the information, or Kullback-Leibler
divergence from the prior to the posterior, was estimated to be 550.2 nats.

>>>>

The marginal likelihood estimate returned by DNS for this data was
$\log(\mathcal{Z}) = -319690.5$, and the information, or Kullback-Leibler
divergence from the prior to the posterior, was estimated to be 593.7 nats.
